A first implementation of Section 3 of ``Bla Parabolic''

### 2019-08-01 Python/time/readme.tex
added tests for damping matrix and unequal in- and out basis
clearing up some things

\begin{enumerate}
  \item Most of the time is spent doing dot products, as can be seen from the code:
    \begin{verbatim}
69  return sum(self.vector[labda] * other[labda] for labda in other.keys()
70             if labda in index_mask)\end{verbatim}
    I am not sure we can do much about this. It makes sense to do it, I think.
  \item We spend a lot of time merging these intervals, probably for constructing
    $\Pi_B$ and $\underline \Pi$. If we think some more about optimizing these
    calls, this will probably go away.
  \item This is a little cryptic but is about creating \texttt{Interval} objects.
    As we are not really doing much with them, possibly it would be better to
    just use \texttt{tuple}s in a next iteration.
  \item This is again to produce the dot-product; see snippet above.
  \item We are lazy and append two disjoint vectors by just adding them; this
    could maybe be improved.
  \item This has to do with creating \texttt{Interval} objects, I think this line
    is because \texttt{Interval} inherits from \texttt{collections.namedtuple}
    which is supposed to be faster than a regular \texttt{object}.
  \item More dot-product business.
  \item This is where we compute $\underline \Pi$, through
    \begin{verbatim}
145  ivs = IntervalSet([basis.scaling_support(index) for index in Pi_B] +
146                    [basis.wavelet_support(index) for index in Lambda_l])
147  return SingleLevelIndexSet({
148      index
149      for index in basis.scaling_indices_on_level(l)
150      if ivs.covers(basis.scaling_support(index))
151  })\end{verbatim}
    as you can see, every call to this is quite expensive. This is because the
    size of $\Delta_\ell$ grows exponentially in $\ell$.\footnote{Actually, for
    nonuniform grids, this is not true but \texttt{haar\_basis.py} and
    \texttt{orthonormal\_basis.py} contain two TODO's in this direction.}
  \item This is overhead of allocating new \texttt{IndexedVector}s at every
    matvec. We could opt to do most matvecs in-place (by passing an
    \texttt{out}-argument).
  \item One can see that only 1.6 seconds is spent sorting, even though quite a
    lot of our (nonoptimized) code uses sorting. This is nice.
\end{enumerate}

@@

>>>>

\begin{enumerate}
  \item Most of the time is spent doing dot products, as can be seen from the code:
    \begin{verbatim}
69  return sum(self.vector[labda] * other[labda] for labda in other.keys()
70             if labda in index_mask)\end{verbatim}
    I am not sure we can do much about this. It makes sense to do it, I think.
  \item We spend a lot of time merging these intervals, probably for constructing
    $\Pi_B$ and $\underline \Pi$. If we think some more about optimizing these
    calls, this will probably go away.
  \item This is a little cryptic but is about creating \texttt{Interval} objects.
    As we are not really doing much with them, possibly it would be better to
    just use \texttt{tuple}s in a next iteration.
  \item This is again to produce the dot-product; see snippet above.
  \item We are lazy and append two disjoint vectors by just adding them; this
    could maybe be improved.
  \item This has to do with creating \texttt{Interval} objects, I think this line
    is because \texttt{Interval} inherits from \texttt{collections.namedtuple}
    which is supposed to be faster than a regular \texttt{object}.
  \item More dot-product business.
  \item This is where we compute $\underline \Pi$, through
    \begin{verbatim}
145  ivs = IntervalSet([basis.scaling_support(index) for index in Pi_B] +
146                    [basis.wavelet_support(index) for index in Lambda_l])
147  return SingleLevelIndexSet({
148      index
149      for index in basis.scaling_indices_on_level(l)
150      if ivs.covers(basis.scaling_support(index))
151  })\end{verbatim}
    as you can see, every call to this is quite expensive. This is because the
    size of $\Delta_\ell$ grows exponentially in $\ell$.\footnote{Actually, for
    nonuniform grids, a much smaller set can be used, but \texttt{haar\_basis.py}
    and \texttt{orthonormal\_basis.py} contain two TODO's in this direction.}
  \item This is overhead of allocating new \texttt{IndexedVector}s at every
    matvec. We could opt to do most matvecs in-place (by passing an
    \texttt{out}-argument).
  \item One can see that only 1.6 seconds is spent sorting, even though quite a
    lot of our (nonoptimized) code uses sorting. This is nice.
\end{enumerate}

@@

In any case, right now,
